---
title: "SelfQuant Report"
author:
date:
output: 
  html_document:
    theme: "darkly"
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE)

# Setup
# LIBRARIES ####
library(tidyverse); library(reshape2)
#library(googlesheets4); library(googledrive)
library(IXIS.Auto)
library(lubridate)
options(freezer = "./RDS")

# Load data
revive(all.1)
```

# L7 Summary

```{r}
all.1 %>% 
  tail(30) %>% 
  select(dim_date, meanHR, RMSSD, weight, hrAvg, hrMax, speedAvg, beatsPerMileAvg, tapRight, `Energy (kcal)`, `Fat (g)`, `Carbs (g)`, `Protein (g)`, cloudCover) %>% 
  melt(id.var = "dim_date") %>% 
  ggplot(aes(x = dim_date, y = value)) +
  geom_line() +
  geom_smooth(method = "loess", span = .3, se = FALSE) +
  scale_x_date(date_breaks = "1 week", minor_breaks = "1 day") +
  facet_grid(variable ~ ., scales = "free_y") +
  ggthemes::theme_solarized()
```


TODO: 

* This section summarizes key biometrics: L7D; LM; %Diff WoW,MoM; LT benchmarks
  * Also include nutrition summary & comparison to goals
  * % of ride time by day & zone (area chart?)
* Primary goal of all of this is to get a read on trend toward overtraining basically, accumulated fatigue
* Also include a "next week" outlook, something like:
  * 7-day forecast (with sunlight, temp, precip, wind)
  * trending out KPIs, including HR, HRV, weight, any efficieny metrics (beats per mile) etc.
  # any flags/alerts, such as too much CHO, too many calories, etc.

   
# HRV

* 14-day trend
* MA
* 7d CV trend


